Cache is King: Presenting a Suite of Blazing-Fast, Correlation Function Code

### 2015-01-13 paper/ms.tex
Trying to fix the dynamic path issue with the python library

\usepackage{amsmath}
\usepackage{aas_macros}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}

@@

@@

\begin{code}
struct cell
{
  DOUBLE *x;
  DOUBLE *y;
  DOUBLE *z;
  int64_t nelements;
}
\end{code}\footnote{Most of the code assumes that the number of galaxies is within INT_MAX $\sim$ 2.1 billion. So, it would appear 
to make no sense that the field inside the struct cell has `nelements' of type int64_t. The reason I have 
chosen to use int64_t is that under C alignment rules 4 bytes of padding would have appended anyway to the struct cell. So, I chose 
to declare `nelements' as an int64_t and used those 4 bytes. Saves some future conversion/coding. }

>>>>

\usepackage{amsmath}
\usepackage{aas_macros}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{color}
\usepackage{listings}

@@

\lstset{
  language=C,                % choose the language of the code
  numbers=left,                   % where to put the line-numbers
  stepnumber=1,                   % the step between two line-numbers.
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
  title=\lstname,                 % show the filename of files included with \lstinputlisting;
}

@@

\footnote{Most of the code assumes that the number of galaxies is within INT_MAX $\sim$ 2.1 billion. So, it would appear 
to make no sense that the field inside the struct cell has `nelements' of type int64_t. The reason I have 
chosen to use int64_t is that under C alignment rules 4 bytes of padding would have appended anyway to the struct cell. So, I chose 
to declare `nelements' as an int64_t and used those 4 bytes. Saves some future conversion/coding. }
